### 2019-12-16 tex/ms.tex
more

For this study, we use a series of 22 exposures. (RA, Dec) =  These exposures were chosen for the following reasons:

\begin{itemize}
\item They were taken during a photometric time period.
\item They were taken in reasonably good seeing -- the FWHM is typically
\item They are taken in a region of high source density
\item They are relatively long GFA exposures (the unique exposure times are 30 seconds and 60 seconds), further improving the density of well-detected sources.
\item Very close to airmass = 1, minimizing impact of any errors in atmospheric transmission component of GFA throughput prediction.
\end{itemize}

@@

\section{PSF-based Aperture Correction}

@@

@@

@@

>>>>

For this throughput study, we use a set of 22 GFA exposures taken on 20191025. The exposures have 21338 $\le$ EXPID $\le$ 21360, with EXPID = 21350 omitted because of its short 1 second exposure time. The program name (PROGRAM keyword header parameter) of this set of exposures is ``dense fields''. These exposures are all centered in the vicinity of (RA, Dec) =  (80$^{\circ}$, 30$^{\circ}$), which is near the Galactic anticenter at ($l_{gal}$, $b_{gal}$) $\sim$ (176, $-4$). These exposures were chosen for the following reasons:

\begin{itemize}
\item They were taken during a photometric time period.
\item They were taken in reasonably good seeing -- the FWHM is typically
\item They are taken in a region of high source density
\item They are relatively long GFA exposures (the unique exposure times are 30 seconds and 60 seconds), further improving the density of well-detected sources.
\item Very close to airmass = 1, minimizing impact of any errors in atmospheric transmission component of GFA throughput prediction.
\item All six cameras worth of guide GFA images are available for all exposures in this sequence.
\item The exposures were dithered at a scale of $\sim$30$''$ per coordinate, so that we are not always sampling the same stars at the same GFA pixel locations during ever single exposure.
\end{itemize}

@@

% mention PSF-based Aperture Correction

@@

% define m_inst

% what is the match radius used?

@@

\subsection{Confirming That ADU Zeropoints Track Gain as Expected}
Amp pairs E/F and G/H should be at approximately the same radial distance from the focal plane center for all cameras. Assuming for each camera that within each of these amp pairs the average vignetting, QE and filter transmission are all the same, then the difference in zeropoint for a 1 ADU source should track the difference in gain, with larger gain corresponding lower (brighter) ADU zeropoint magnitude. Based on these assumptions and the measured gains, we can predict the difference in zeropoints for amp pairs E/F and G/H and check whether this correlates with the measured differences in zeropoints. The two scatter plots below summarize this analysis, with one plot for the E/F amp pair and one plot for the G/H amp pair. Each data point in each plot represents one guide GFA camera. The plots show that the measured ADU zeropoints do track fairly well with expectations based on the gain differences. The lab-measured GFA acceptance report gains were used in making these plots.

\begin{figure*}[ht]
        \includegraphics[width=7.0in]{zp_adu_gain_correlation-EF.png}
    \caption{test}
    \label{fig:ampsEF}
\end{figure*}

\begin{figure*}[ht]
        \includegraphics[width=7.0in]{zp_adu_gain_correlation-GH.png}
    \caption{test}
    \label{fig:ampsEF}
\end{figure*}

@@

% say what the vertical yellow line means...
